---
title: "FFELthemes"
author: "UNBC Freshwater Fish Ecology Laboratory"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FFELthemes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(ggplot2)
library(FFELthemes) # Even without downloading the package, if you run devtools::build_vignette(), R will temporarily install FFELthemes. To actually have access to the functions for the vignette building, you'll need to use the library() command. This is a bit more confusing once you are actually creating a vignette for CRAN.
```

#### Development Notes:

-   For package development:

    -   Ajust functions and vignette.

    -   Use `devtools::document()`, to update documentation and NAMESPACCE.

    -   Use `devtools::build_vignette()` to build and view the vignette in the `docs` folder.

    -   Use `devtools::loal_all()` to temporily load the package and test functionality and help files.

    -   Use `devtools::check()` to make sure your additions are working and don't violate the package standards/requirements.

-   It would be great to develop additional colour schemes and create more applicable/beautiful `ggplot` examples.

## Overview

The `FFELthemes` package generates custom themes and colour palettes for `ggplot2` plot objects.

## Installation

`FFELthemes` is installed from the FFEL GitHub page.

```{r installation, eval = FALSE}
devtools::install_github("Freshwater-Fish-Ecology-Laboratory/FFELthemes")
library(FFELthemes)
```

## Themes

Apply a custom theme by adding `+ theme_ffel()` to a `ggplot2` object.

```{r theme example, fig.height=5, fig.width=7}
ggplot(mtcars, aes(mpg, disp)) +
  geom_point(size = 4) +
  facet_wrap(~cyl) +
  theme_ffel()
```

### Adjusting Base Font Size

The argument `base_size` from `theme_ffel` scales the size of plot text. The default size is 16, which is appropriate \~6 inch plots. For very large or small plots, `base_size` can be adjusted for readability.

```{r base size example, fig.height=5, fig.width=7}
ggplot(mtcars, aes(mpg, disp)) +
  geom_point(size = 4) +
  facet_wrap(~cyl) +
  theme_ffel(base_size = 10)
```

### Overwriting the Theme

Additional `theme` arguments can be used to overwrite portions of `theme_ffel`.

```{r theme overwrite, fig.height=5, fig.width=7}
ggplot(mtcars, aes(mpg, disp)) +
  geom_point(size = 4) +
  facet_wrap(~cyl) +
  theme_ffel() +
  theme(axis.text.x = element_text(color = "blue"),
        panel.grid.major = element_line(),
        panel.grid.minor = element_line())
```

## Colours

Several colour palettes are available using the FFEL colour scheme.

```{r show colours}
scales::show_col(ffel_colours)
```

The colours can used in discrete or continuous applications. The colours are used by a palette generating function to create complementary palettes.

Individual colours can be selected by name to customize plots.

```{r select colours, fig.height=5, fig.width=7}
ggplot(mtcars, aes(hp, mpg)) +
  geom_point(color = ffel_cols("metalic blue"),
             size = 3) +
  theme_ffel()
```

Palettes can be selected by name and applied to fill or colour objects.

```{r apply colour palettes, fig.height=5, fig.width=7}
# View available palettes
ffel_palettes

ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  scale_fill_ffel(palette = "main") +
  theme_ffel() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_colour_ffel(discrete = FALSE, palette = "two") +
  theme_ffel()
```
